INTELLIGENT SYSTEMS

### 2021-04-10 slides.tex
start slide paper5

>>>>

\section{Paper 5}
\subsection{\emph{"An End-to-End Multi-Task and Fusion CNN for Inertial-Based Gait Recognition"}}

\begin{frame}{INTRODUCTION}
    The gait recognition is an activity used in the medical, security and 
    authentication fields. The following paper shows a convolutional neural 
    network (CNN) which takes as input a series of inertial data, coming 
    from different sensors, and produces as output a prediction useful for 
    recognizing a subject.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper5/usecase.png}
        \centering
        \caption{A preview of how the model works.}
        \label{fig:preview}
    \end{figure}
\end{frame}

\begin{frame}{RELATED WORK}
